---
title: "Nasal bacteriomes"
output:
  html_document:
    toc: true
    toc_depth: 2
    theme: cerulean
 
date: "2022-12-27"
---

# Packages loading 

```{r}
library(phyloseq)
library(cowplot)
library(picante)
library(TSA)
library(multcomp)
library(microbiome)
library(mvabund)
library(geepack)
library(doBy)
library(lattice)
library(MuMIn)
library("DESeq2")
library(tidyverse)
library(stringr)
library(fantaxtic)
```


```{r}
readRDS(file = "nasal_bacteriome.RDS") -> ps1
```

```{r}
ps1
```

# Filter samples and ASVs 

### remove singletons
```{r}
ps1 <- prune_taxa(taxa_sums(ps1) > 1, ps1)
ps1
```
### remove samples with less than 1000 reads
```{r}
ps1 = prune_samples(sample_sums(ps1) >= 1000, ps1)
ps1
min(colSums(otu_table(ps1)))

summarize_phyloseq(ps1)
```

# Core Microbiome 
```{r}
ps1.core <- core(ps1, detection = 0, prevalence = 0.9)
core.taxa <- taxa(ps1.core);core.taxa
class(core.taxa)
```
### Get the taxonomy data
```{r}
tax.mat <- tax_table(ps1.core)
tax.df <- as.data.frame(tax.mat)
```
### Add the ASVs to last 
```{r}
tax.df$ASV <- rownames(tax.df)
```
### Select taxonomy of only. Those ASVs that are core members based on the thresholds that were used.
```{r}
core.taxa.class <- dplyr::filter(tax.df, rownames(tax.df) %in% core.taxa)
knitr::kable(head(core.taxa.class))
knitr::kable(core.taxa.class)
```
### estimate read proportions for the core
```{r}
rank_names(ps1.core, errorIfNULL=TRUE) 
taxon <- tax_glom(ps1.core, taxrank = "Species")
table_all<-cbind(tax_table(taxon),otu_table(taxon))
table_all_t<-t(data.matrix(table_all))
write.csv(table_all_t,file="core_N.csv")
summarize_phyloseq(ps1)
```
# Data normalization
```{r}
diagdds = phyloseq_to_deseq2(ps1, ~season) # Any variable of the metadata would work to create the DESeq object
```
### Calculate geometric means

```{r}
gm_mean = function(x, na.rm=TRUE){
  exp(sum(log(x[x > 0]), na.rm=na.rm) / length(x))
}
geoMeans = apply(counts(diagdds), 1, gm_mean)
```
### Estimate size factors
```{r}
diagdds = estimateSizeFactors(diagdds, geoMeans = geoMeans)
```
### Get normalized read counts
```{r}
normcounts <- counts(diagdds, normalized = TRUE)
```
### Round read counts
```{r}
round(normcounts, digits = 0) -> normcountsrd
```
### Transform matrix of normalized counts to phyloseq object
```{r}
otu_table(normcountsrd, taxa_are_rows = TRUE) -> ncr
```
### Replace otu_table in original phyloseq object
```{r}
otu_table(ps1) <- ncr
```
# Estimate alpha-diversity including pd 

```{r}
otuD<-as.data.frame(t(otu_table(ps1)))
phylodiversityRAREF_Q<-pd(otuD, phy_tree(ps1), include.root=TRUE) ### Phylogenetic diversity. Include root=True tree rooted via midpoint
diversityRAREF_Q<-estimate_richness(ps1)
diversityRAREF_Q1<-cbind(sample_data(ps1),diversityRAREF_Q,phylodiversityRAREF_Q) 
```

```{r}
library(ggpubr)
```

```{r}
my_comparisons <- list(c("AS", "CT"),c("AR", "CT"),c("ARAS", "CT"),c("AS", "AR"),c("AS", "ARAS"),c("AR", "ARAS")) # List here the group pairs to compare statistically
```

```{r}
compare_means(formula = Chao1~asthma_rhinitis1,data = diversityRAREF_Q1, method = "wilcox.test", exact= FALSE)
chao <- ggplot(diversityRAREF_Q1, aes(factor(asthma_rhinitis1), Chao1))
chao2<-chao + geom_boxplot(aes(fill = factor(asthma_rhinitis1)),outlier.colour = "black", outlier.size = 0.2)+ geom_jitter(size=0.2,shape=1)+panel_border(colour = "black", size = 0.5)+ ggtitle("Chao1 richness")+labs(y = "Chao1 richness") + stat_compare_means(mapping = NULL, comparisons = my_comparisons, hide.ns = FALSE, label = "p.signif",  label.x = NULL, label.y = NULL, exact =FALSE)
```

```{r}
compare_means(formula = Shannon~asthma_rhinitis1,data = diversityRAREF_Q1, method = "wilcox.test", exact= FALSE)
shan <- ggplot(diversityRAREF_Q1, aes(factor(asthma_rhinitis1), Shannon))
shan2<-shan + geom_boxplot(aes(fill = factor(asthma_rhinitis1)),outlier.colour = "black", outlier.size = 0.2)+ geom_jitter(size=0.2,shape=1)+panel_border(colour = "black", size = 0.5)+ ggtitle("Shannon diversity")+labs(y = "Shannon diversity") + stat_compare_means(mapping = NULL, comparisons = my_comparisons, hide.ns = FALSE, label = "p.signif",  label.x = NULL, label.y = NULL, exact =FALSE)
```

```{r}
compare_means(formula = ACE~asthma_rhinitis1,data = diversityRAREF_Q1, method = "wilcox.test", exact= FALSE)
ACE <- ggplot(diversityRAREF_Q1, aes(factor(asthma_rhinitis1), ACE))
ACE2<- ACE + geom_boxplot(aes(fill = factor(asthma_rhinitis1)),outlier.colour = "black", outlier.size = 0.2)+ geom_jitter(size=0.2,shape=1)+panel_border(colour = "black", size = 0.5)+ ggtitle("ACE diversity")+labs(y = "ACE diversity") + stat_compare_means(mapping = NULL, comparisons = my_comparisons, hide.ns = FALSE, label = "p.signif",  label.x = NULL, label.y = NULL, exact =FALSE)
```

```{r}
compare_means(formula = PD~asthma_rhinitis1,data = diversityRAREF_Q1, method = "wilcox.test", exact= FALSE)
phyl <- ggplot(diversityRAREF_Q1, aes(factor(asthma_rhinitis1), PD))
phyl2<- phyl + geom_boxplot(aes(fill = factor(asthma_rhinitis1)),outlier.colour = "black", outlier.size = 0.2)+ geom_jitter(size=0.2,shape=1)+panel_border(colour = "black", size = 0.5)+ ggtitle("Phylogenetic diversity")+labs(y = "Phylogenetic  diversity") + stat_compare_means(mapping = NULL, comparisons = my_comparisons, hide.ns = FALSE, label = "p.signif",  label.x = NULL, label.y = NULL, exact =FALSE)

plot_grid(chao2, shan2, ACE2, phyl2, nrows=2, cols=2, align = "v")  
```


# Estimate beta-diversity 

### Sample pairs

```{r}
ps2 <- subset_samples(ps1, asthma_rhinitis1 == "AR" | asthma_rhinitis1 == "CT"); ps2

otuD<-as.data.frame(t(otu_table(ps2)))
diversityRAREF_Q1<-cbind(sample_data(ps2)) 

uniun<-phyloseq::distance(ps2, method="unifrac")
uniweigh<-phyloseq::distance(ps2, method="wunifrac")
brayd<-phyloseq::distance(ps2, method="bray")
jaccd<-phyloseq::distance(ps2, method="jaccard")

t1<-adonis2(uniun~diversityRAREF_Q1$asthma_rhinitis1, perm=10000); t1
t1<-adonis2(uniweigh~diversityRAREF_Q1$asthma_rhinitis1, perm=10000); t1
t1<-adonis2(brayd~diversityRAREF_Q1$asthma_rhinitis1, perm=10000); t1
t1<-adonis2(jaccd~diversityRAREF_Q1$asthma_rhinitis1, perm=10000); t1
```
### All pairs

```{r}
uniun<-phyloseq::distance(ps1, method="unifrac")
uniweigh<-phyloseq::distance(ps1, method="wunifrac")
brayd<-phyloseq::distance(ps1, method="bray")
jaccd<-phyloseq::distance(ps1, method="jaccard")
```
# PCoA plots
```{r}
p1 = phyloseq::plot_ordination(ps1, ordinate(ps1, method="PCoA", dist="unifrac", weighted=TRUE), type = "samples", color = "asthma_rhinitis1") # label="patient" 
p1a=p1 + geom_point(size = 2) + ggtitle("PCoA Weigthed UNIFRAC") 
p2 = phyloseq::plot_ordination(ps1, ordinate(ps1, method="PCoA", dist="unifrac"), type = "samples", color = "asthma_rhinitis1") # label="patient" 
p2a=p2 + geom_point(size = 2) + ggtitle("PCoA Unweigthed UNIFRAC") 
p3 = phyloseq::plot_ordination(ps1, ordinate(ps1, method="PCoA", dist="brayd"), type = "samples", color = "asthma_rhinitis1") 
p3a=p3 + geom_point(size = 2) + ggtitle("PCoA Bray-Curtis") 
p4 = phyloseq::plot_ordination(ps1, ordinate(ps1, method="PCoA", dist="jaccd"), type = "samples", color = "asthma_rhinitis1") 
p4a=p4 + geom_point(size = 2) + ggtitle("PCoA Jaccard") 

p1a
p2a
p3a
p4a
plot_grid(p1a, p2a, p3a, p4a, ncol = 2, nrows=2, align = "v")
```


# Statistical analyses of taxa % and other variables

```{r}
bygenus <- tax_glom(ps1, taxrank = "Phylum") # ASV in taxa_lineage below = phylum name

bygenus.tr <- transform_sample_counts(bygenus, function (x) x/sum(x))
bygenus.tr.f <- filter_taxa(bygenus.tr, function (x) mean(x) > 1e-2, TRUE) # filter taxa below 5%
taxa_names(bygenus.tr.f)
taxa_lineage <- tax_table(bygenus.tr.f);taxa_lineage
taxa_abun<-as.data.frame(t(otu_table(bygenus.tr.f)))
taxa_abun1<-cbind(sample_data(ps1),taxa_abun) 

```

```{r}
my_comparisons <- list(c("AS", "CT"),c("AR", "CT"),c("ARAS", "CT"),c("AS", "AR"),c("AS", "ARAS"),c("AR", "ARAS")) # List here the group pairs to compare statistically
```

```{r}
library(ggpubr)
```
### Run text for each dominant ASV corresponding to phyla and genera

```{r}
compare_means(formula = ASV39~asthma_rhinitis1, data = taxa_abun1, method = "wilcox.test", exact= FALSE)
```


# PICRUSt2 commands

### Bash section 

```{bash eval= FALSE}
place_seqs.py -s ASVs.fasta -o out.tre -p 9 --intermediate intermediate/place_seqs
```

```{bash eval= FALSE}
hsp.py -i 16S -t ASV_tree.txt -o marker_predicted_and_nsti.tsv.gz -p 9 -n
```

```{bash eval= FALSE}
hsp.py -i EC -t ASV_tree.txt -o marker_predicted_and_nsti.tsv.gz -p 9 -n
```

```{bash eval= FALSE}
metagenome_pipeline.py -i ASVs.biom -m marker_predicted_and_nsti.tsv.gz -f EC_predicted.tsv.gz -o EC_metagenome_out --strat_out -p 9
```

```{bash eval= FALSE}
pathway_pipeline.py -i EC_metagenome_out/pred_metagenome_contrib.tsv.gz -o pathways_out -p 9
```

```{bash eval= FALSE}
add_descriptions.py -i EC_metagenome_out/pred_metagenome_unstrat.tsv.gz -m EC -o EC_metagenome_out/pred_metagenome_unstrat_descrip.tsv.gz
```

```{bash eval= FALSE}
add_descriptions.py -i pathways_out/path_abun_unstrat.tsv.gz -m METACYC -o pathways_out/path_abun_unstrat_descrip.tsv.gz
```

### End of bash section



```{r}
library("data.table")
library("ComplexHeatmap")
library("RColorBrewer")
library("circlize")
```



### Laod pathway table

```{r}
pws_table <- fread("path_abun_unstrat_descrip.tsv.gz")
```


### Load phyloseq object

```{r} 
nasal_CT_ps <- read_rds("nasal_pathway_CT.RDS")
nasal_AR_ps <- read_rds("nasal_pathway_AR.RDS")
nasal_ARAS_ps <- read_rds("nasal_pathway_ARAS.RDS")
```

```{r}
merged_nasal <- merge_phyloseq(nasal_CT_ps, nasal_AR_ps, nasal_ARAS_ps)

merged_nasal <- subset_samples(merged_nasal, sample_names(merged_nasal) != "NO67")

sample_data(merged_nasal)$sample_code <- gsub("_S.+$","",sample_data(merged_nasal)$sample_code)
```

```{r}
my_design <- ~ sex + age + asthma_rhinitis
```

```{r}
my_pw_counts_nasal <- pws_table %>%
  dplyr::select(pathway, description, sample_data(merged_nasal)$sample_code)


only_cs_my_pw_nasal <- my_pw_counts_nasal[,-c(1:2)]


ds_obj_nasal <- DESeqDataSetFromMatrix(countData = round(only_cs_my_pw_nasal),
                                       colData = sample_data(merged_nasal),
                                       design = my_design)


ds_nasal_analysis <- DESeq(ds_obj_nasal)
```


```{r}
ARAS_vs_CT_wald <- results(ds_nasal_analysis, contrast = c("asthma_rhinitis", "AR", "NO"))

AR_vs_CT_wald <- results(ds_nasal_analysis, contrast = c("asthma_rhinitis", "RN", "NO"))

ARAS_vs_AR_wald <- results(ds_nasal_analysis, contrast = c("asthma_rhinitis", "AR", "RN"))
```



### Subset for p-value < 0.05

```{r}
nasal_ARAS_CT_sigres <- ARAS_vs_CT_wald %>%
  data.frame() %>%
  rownames_to_column(var = "pathway") %>%
  as_tibble() %>%
  dplyr::filter(padj < 0.05)

```

```{r}
nasal_AR_CT_sigres <- AR_vs_CT_wald %>%
  data.frame() %>%
  rownames_to_column(var = "pathway") %>%
  as_tibble() %>%
  dplyr::filter(padj < 0.05)

```

```{r}
nasal_ARAS_vs_AR_sigres <- ARAS_vs_AR_wald %>%
  data.frame() %>%
  rownames_to_column(var = "pathway") %>%
  as_tibble() %>%
  dplyr::filter(padj < 0.05)

```

```{r}
nasal_ARAS_CT_sigres$pathway <- pws_table$description[as.numeric(nasal_ARAS_CT_sigres$pathway)]


nasal_ARAS_CT_sigres <- nasal_ARAS_CT_sigres[order(nasal_ARAS_CT_sigres$log2FoldChange, decreasing = TRUE),]


nasal_ARAS_CT_sigres <- nasal_ARAS_CT_sigres[abs(nasal_ARAS_CT_sigres$log2FoldChange) >= 2,]


nasal_ARAS_CT_sigres

```

```{r}
nasal_AR_CT_sigres$pathway <- pws_table$description[as.numeric(nasal_AR_CT_sigres$pathway)]

nasal_AR_CT_sigres <- nasal_AR_CT_sigres[order(nasal_AR_CT_sigres$log2FoldChange, decreasing = TRUE),]

nasal_AR_CT_sigres <- nasal_AR_CT_sigres[abs(nasal_AR_CT_sigres$log2FoldChange) >= 2,]

nasal_AR_CT_sigres
```


```{r}
nasal_ARAS_vs_AR_sigres$pathway <- pws_table$description[as.numeric(nasal_ARAS_vs_AR_sigres$pathway)]
nasal_ARAS_vs_AR_sigres <- nasal_ARAS_vs_AR_sigres[order(nasal_ARAS_vs_AR_sigres$log2FoldChange,
                                                     decreasing = T),]

nasal_ARAS_vs_AR_sigres <- nasal_ARAS_vs_AR_sigres[abs(nasal_ARAS_vs_AR_sigres$log2FoldChange) >= 2,]
nasal_ARAS_vs_AR_sigres
```




## From these last objects, prepare log2foldchange vectors



### Log2fc for ARAS vs CT

```{r}
log2fc_nasal_ARAS_CT <- nasal_ARAS_CT_sigres$log2FoldChange %>%
  as.matrix()


colnames(log2fc_nasal_ARAS_CT) <- "log2FC"

```

```{r}
log2fc_nasal_ARAS_CT_colors <- colorRamp2(c(min(log2fc_nasal_ARAS_CT),0,max(log2fc_nasal_ARAS_CT)),
                                        c("blue","white","orange"))



hm_nasal_CT_ARAS_fc <- Heatmap(log2fc_nasal_ARAS_CT, cluster_rows = F, row_labels = nasal_ARAS_CT_sigres$pathway,
                             col = log2fc_nasal_ARAS_CT_colors, width = unit(30,"mm"),
                             cell_fun = function(j,i,x,y,w,h,col){
                               grid.text(round(log2fc_nasal_ARAS_CT[i,j],2),x,y)
                             }, name = "log2FC", column_labels = "", height = unit(280,
                                                                                   "mm"))



draw(hm_nasal_CT_ARAS_fc, heatmap_legend_side = "left")
```


### Log2fc for AR and CT


```{r}
log2fc_nasal_AR_CT <- nasal_AR_CT_sigres$log2FoldChange %>%
  as.matrix()

colnames(log2fc_nasal_AR_CT) <- "log2FC"

log2fc_nasal_AR_CT_colors <- colorRamp2(c(min(log2fc_nasal_AR_CT),0,max(log2fc_nasal_AR_CT)),
                                        c("blue","white","orange"))


hm_nasal_CT_AR_fc <- Heatmap(log2fc_nasal_AR_CT, cluster_rows = F, row_labels = nasal_AR_CT_sigres$pathway,
                             width = unit(30,"mm"), col = log2fc_nasal_AR_CT_colors,
                             cell_fun = function(i,j,x,y,w,h,col){
                               grid.text(round(log2fc_nasal_AR_CT[j,i],2),x,y)
                             }, name = "log2FC", column_labels = "", height = unit(280,"mm"))


draw(hm_nasal_CT_AR_fc, heatmap_legend_side = "left")
```




### Log2fc for ARAS vs AR

```{r}
log2fc_nasal_ARAS_AR <- nasal_ARAS_vs_AR_sigres$log2FoldChange %>%
  as.matrix()

colnames(log2fc_nasal_ARAS_AR) <- "log2FC"


log2fc_nasal_ARAS_AR_colors <- colorRamp2(c(min(log2fc_nasal_ARAS_AR),0,max(log2fc_nasal_ARAS_AR)),
                                        c("blue","white","orange"))


hm_nasal_ARAS_AR_fc <- Heatmap(log2fc_nasal_ARAS_AR, cluster_rows = F, row_labels = nasal_ARAS_vs_AR_sigres$pathway,
                             width = unit(30,"mm"), col = log2fc_nasal_ARAS_AR_colors,
                             cell_fun = function(i,j,x,y,w,h,col){
                               grid.text(round(log2fc_nasal_ARAS_AR[j,i],2),x,y)
                             }, name = "log2FC", column_labels = "")


draw(hm_nasal_ARAS_AR_fc, heatmap_legend_side = "left")

```


# Arrange phyloseq objects for network analysis

```{r}
nasal_ARAS <- read_rds("nasal_pathway_ARAS.RDS")
nasal_AR <- read_rds("nasal_pathway_AR.RDS")
nasal_CT <- read_rds("nasal_pathway_CT.RDS")
```

```{r}
library("microbiomeutilities")
```

### Define best hit of classification
```{r}
nasal_ARAS <- format_to_besthit(nasal_ARAS, prefix = "")
nasal_AR <- format_to_besthit(nasal_AR, prefix = "")
nasal_CT <- format_to_besthit(nasal_CT, prefix = "")
```

### Agglomerate taxa at species level
```{r}
nasal_ARAS <- tax_glom(nasal_ARAS, taxrank = rank_names(nasal_ARAS)[7])
nasal_AR <- tax_glom(nasal_AR, taxrank = rank_names(nasal_AR)[7])
nasal_CT <- tax_glom(nasal_CT, taxrank = rank_names(nasal_CT)[7])
```

### Filter out low prevalent taxa

```{r}
library("metagMisc")
```

```{r}
nasal_ARASprv <- phyloseq_filter_prevalence(nasal_ARAS, prev.trh = 0.10 , abund.trh = 3,
                                          threshold_condition = "OR", abund.type = "median")

nasal_ARprv <- phyloseq_filter_prevalence(nasal_AR, prev.trh = 0.10 , abund.trh = 3,
                                          threshold_condition = "OR", abund.type = "median")

nasal_CTprv <- phyloseq_filter_prevalence(nasal_CT, prev.trh = 0.10 , abund.trh = 3,
                                          threshold_condition = "OR", abund.type = "median" )

```

### Remove non prokaryotic ASVs

```{r}
taxa_forfilter <- c("Chloroplast", "Mitochondria","Eukaryota")

ps_list = list(nasal_ARASprv, nasal_ARprv, nasal_CTprv)

for (i in 1:length(ps_list)) { 
  ps_list[[i]] <- subset_taxa(ps_list[[i]],
                              !Domain %in% taxa_forfilter & 
                                !Phylum %in% taxa_forfilter & 
                                !Class %in% taxa_forfilter & 
                                !Order %in% taxa_forfilter & 
                                !Family %in% taxa_forfilter & 
                                !Genus %in% taxa_forfilter )   }

nasalARAS <- ps_list[[1]]
nasalAR <- ps_list[[2]]
nasalCT <- ps_list[[3]]
```

```{r}
library("SpiecEasi")  
```

# Networks calculation using neighborhood selection (mb) method



```{r}
nasalCT_net = spiec.easi(nasalCT, method = "mb", nlambda = 20,
                         lambda.min.ratio = 1e-2, pulsar.params = list(rep.num=50,
                                                                       ncores=11))


nasalARAS_net = spiec.easi(nasalARAS, method = "mb", nlambda = 20,
                         lambda.min.ratio = 1e-2, pulsar.params = list(rep.num=50,
                                                                       ncores=11))


nasalAR_net = spiec.easi(nasalAR, method = "mb", nlambda = 20,
                         lambda.min.ratio = 1e-2, pulsar.params = list(rep.num=50,
                                                                       ncores=11))

# the resulting variables were stored in RDS format and exported for local analysis
```




### Retrieve adjacency matrices 

```{r}
library("NetCoMi")
```


```{r}
adj_nasalARAS <- symBeta(getOptBeta(nasalARAS_net), mode = "maxabs") %>%
  as.matrix()

rownames(adj_nasalARAS) <- colnames(otu_table(nasalARAS)) 
colnames(adj_nasalARAS) <- colnames(otu_table(nasalARAS))

```

```{r}
adj_nasalAR <- symBeta(getOptBeta(nasalAR_net), mode = "maxabs") %>%
  as.matrix()

rownames(adj_nasalAR) <- colnames(otu_table(nasalAR))
colnames(adj_nasalAR) <- colnames(otu_table(nasalAR))
```

```{r}
adj_nasalCT <- symBeta(getOptBeta(nasalCT_net), mode = "maxabs") %>%
  as.matrix()

rownames(adj_nasalCT) <- colnames(otu_table(nasalCT))
colnames(adj_nasalCT) <- colnames(otu_table(nasalCT))
```


### Construct the networks

```{r}
nasalARAS_netcomi <- netConstruct(data = adj_nasalARAS,
                                normMethod = "none", zeroMethod = "none",
                                sparsMethod = "none", dataType = "condDependence",
                                verbose = 3, seed = 1234)
```

```{r}
nasalAR_netcomi <- netConstruct(data = adj_nasalAR,
                                normMethod = "none", zeroMethod = "none",
                                sparsMethod = "none", dataType = "condDependence",
                                verbose = 3, seed = 1234)
```

```{r}
nasalCT_netcomi <- netConstruct(data = adj_nasalCT,
                                normMethod = "none", zeroMethod = "none",
                                sparsMethod = "none", dataType = "condDependence",
                                verbose = 3, seed = 1234)
```



# Analyze the networks 

```{r}
nasalARAS_analyzed <- netAnalyze(nasalARAS_netcomi, centrLCC = FALSE, avDissIgnoreInf = TRUE, 
                               hubPar = "degree", hubQuant = 0.90,
                               normDeg = TRUE, normBetw = TRUE, normEigen = TRUE, verbose = 2)

```

```{r}

nasalAR_analyzed <- netAnalyze(nasalAR_netcomi, centrLCC = FALSE, avDissIgnoreInf = TRUE,
                               hubPar = "degree", hubQuant = 0.90,
                               normDeg = TRUE, normBetw = TRUE, normEigen = TRUE, verbose = 2)

```


```{r}
nasalCT_analyzed <- netAnalyze(nasalCT_netcomi, centrLCC = FALSE, avDissIgnoreInf = TRUE,
                               hubPar = "degree", hubQuant = 0.90,
                               normDeg = TRUE, normBetw = TRUE, normEigen = TRUE, verbose = 2)

```




## Label the networks nodes by the best hit and remove unwanted characters


### Nasal ARAS labels

```{r}
tax_nasalARAS <- tax_table(nasalARAS) %>%
  as.data.frame() %>%
  dplyr::mutate(lab = paste(Genus, Species, sep = " ")) %>%
  dplyr::select(-best_hit)

tax_nasalARAS$lab <- gsub("g__.+$", "", tax_nasalARAS$lab)
tax_nasalARAS$lab <- gsub("f__.*?\\s", "", tax_nasalARAS$lab)
tax_nasalARAS$lab <- gsub("f__","", tax_nasalARAS$lab)
tax_nasalARAS$lab <- gsub("o__.*?\\s", "", tax_nasalARAS$lab)
tax_nasalARAS$lab <- gsub("o__", "", tax_nasalARAS$lab)



labels_nasalARAS <- tax_nasalARAS$lab
names(labels_nasalARAS) <- rownames(tax_nasalARAS)

```



### Nasal AR labels

```{r}
tax_nasalAR <- tax_table(nasalAR) %>%
  as.data.frame() %>%
  dplyr::mutate(lab = paste(Genus, Species, sep = " ")) %>%
  dplyr::select(-best_hit)

tax_nasalAR$lab <- gsub("g__.+$", "", tax_nasalAR$lab)
tax_nasalAR$lab <- gsub("f__.*?\\s", "", tax_nasalAR$lab)
tax_nasalAR$lab <- gsub("f__","", tax_nasalAR$lab)
tax_nasalAR$lab <- gsub("o__.*?\\s", "", tax_nasalAR$lab)
tax_nasalAR$lab <- gsub("o__", "", tax_nasalAR$lab)


labels_nasalAR <- tax_nasalAR$lab
names(labels_nasalAR) <- rownames(tax_nasalAR)
```



### Nasal CT labels

```{r}
tax_nasalCT <- tax_table(nasalCT) %>%
  as.data.frame() %>%
  dplyr::mutate(lab = paste(Genus, Species, sep = " ")) %>%
  dplyr::select(-best_hit)

tax_nasalCT$lab <- gsub("g__.+$", "", tax_nasalCT$lab)
tax_nasalCT$lab <- gsub("f__.*?\\s", "", tax_nasalCT$lab)
tax_nasalCT$lab <- gsub("f__","", tax_nasalCT$lab)
tax_nasalCT$lab <- gsub("o__.*?\\s", "", tax_nasalCT$lab)
tax_nasalCT$lab <- gsub("o__", "", tax_nasalCT$lab)


labels_nasalCT <- tax_nasalCT$lab
names(labels_nasalCT) <- rownames(tax_nasalCT)
```


# Plot nasal bacteriome networks and color nodes by clusters/modules

```{r}
nasalARAS_circle <- plot(nasalARAS_analyzed, cexNodes = 1.3, 
                       cexHubLabels = 1.9 , cexLabels = 2.7, cexTitle = 2.5, nodeColor = "cluster",
                       cexHubs = 1.6, rmSingles = "all", 
                       repulsion = 2.8, 
                       layout = "layout_nicely", labels = labels_nasalARAS) 
```

```{r}

nasalAR_circle <- plot(nasalAR_analyzed, cexNodes = 1.3, 
                       cexHubLabels = 1.9 , cexLabels = 2.7, cexTitle = 2.5, nodeColor = "cluster",
                       cexHubs = 1.6, rmSingles = "all", 
                       repulsion = 2.8, 
                       layout = "layout_nicely", labels = labels_nasalAR) 

```


```{r}
nasalCT_circle <- plot(nasalCT_analyzed, cexNodes = 1.3, 
                       cexHubLabels = 1.9 , cexLabels = 2.7, cexTitle = 2.5, nodeColor = "cluster",
                       cexHubs = 1.6, rmSingles = "all", 
                       repulsion = 2.8, 
                       layout = "layout_nicely", labels = labels_nasalCT )

```
